---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dsci310utils

<!-- badges: start -->

[![codecov](https://codecov.io/gh/DSCI-310-2024/dsci310utils/branch/main/graph/badge.svg)](https://codecov.io/gh/DSCI-310-2024/dsci310utils)

<!-- badges: end -->

The goal of dsci310utils is to simplifying the data analysis workflow. The package focuses on data extraction, data preprocessing, confusion matrix data summarization, and visualization. The package includes functions for:

-   Extracting the files in a zipped folder that is downloaded from a URL.
-   Cleaning the data frame and returns a cleaned data frame with only the required columns.
-   Creating a histogram with the given data.
-   Creating and Write a Summary of the Confusion Matrix

## Installation

You can install the development version of dsci310utils from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310-2024/dsci310_utils")
```

## Example

This is a basic example which shows you how to solve a common problem:

1.  The `unzip_URL()` is designed to download and extract files from a zipped folder located at a specified URL directly into a target directory. This utility function simplifies the process of obtaining zipped data from the internet by automating both the download and extraction steps, saving time and streamlining data preparation tasks.

    For convenience, and to illustrate its usage without executing the extraction in this documentation, the command is presented in comment form below:

    ```{r example1}
    #Since thsi function will extract files to target directory, for convince, we just show the comment how to use it 

    # Example usage:
    #unzip_URL('https://archive.ics.uci.edu/static/public/332/online+news+popularity.zip', "data/")

    ```

```{=html}
<!-- -->
```
2.  The `clean_data()` function is designed to streamline the preprocessing of data frames. This function is particularly beneficial when dealing with large datasets, where only specific columns are needed for analysis.

```{r example2}
library(dsci310utils)

required_columns <- c("shares", "num_hrefs", "is_popular")

share_data <- data.frame(
  shares = c(593, 711, 1500, 1200, 505, 855),
  num_hrefs = c(4, 3, 3, 9, 19, 2),
  num_imgs = c(1, 1, 1, 1, 20, 0),
  num_videos = c(0, 0, 0, 0, 0, 0),
  is_popular = c(0, 0, 1, 0, 0, 0)
)

clean_data_frame <- clean_data(share_data, required_columns)

head(clean_data_frame)

```

3.  The `make_histogram()` create a histogram with the given data. The function simplifies the process of creating histograms, requiring only the necessary variables without worrying about the underlying plotting details.

```{r example3}

clean_data_frame$is_popular <- factor(clean_data_frame$is_popular)

make_histogram(clean_data_frame, "num_hrefs", "is_popular","number of shares", "Histogram of shares")
```

4.  The `create_conf_mat_summary()` function calculates precision, recall, and accuracy using the components of a given confusion matrix (TP, FP, FN, TN). It then records these summary statistics into a CSV file, which is saved in the specified directory. Utilizing this function can significantly enhance the evaluation process of predictive models by offering a quick and reliable method for assessing the performance of prediction models.

```{r example4}
temp_dir <- tempdir()
create_conf_mat_summary(TP = 100, FP = 10, FN = 5, TN = 85, output_directory = temp_dir)


```

### Running the test

Tests are run using the testthat command at the root of the project after finishing the installation and library part.

Run the following command in the R terminal:

```         
testthat::test_dir("tests")
```

Check out the [test sites](https://github.com/DSCI-310-2024/dsci310utils/tree/main/tests/testthat) that can find more information.


### Licenses

The software content of this template repository licensed under the [MIT License](https://spdx.org/licenses/MIT.html). See the [license file](LICENSE.md) for more information.